\documentclass{article}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{geometry}
\geometry{margin=1in}

\title{Optimization Report}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Objective}
To find a parameter vector $\mathbf{x}^*$ minimizing the discrepancy between $\varphi(\mathbf{x}; t)$ and $\sin(t)$ over the interval $[-2\pi, 2\pi]$, using various optimization algorithms starting from scaled initial guesses.

\section*{Method 1: BFGS}
\textbf{General Behavior:} BFGS showed some sensitivity to the initial scaling. Moderate scales (0.75) performed best, with low distances to $\mathbf{x}^*$ and stable convergence behavior. At higher scales, convergence worsened.

\begin{tabular}{cccccc}
\toprule
Run & Scale & Distance to $\mathbf{x}^*$ & $\ell_k$ & $q_k$ & Runtime (s) \\
\midrule
1 & 0.5  & 13.18 & 1.0086 & 0.0772 & 3.20 \\
2 & 0.75 & 5.21  & 1.0000 & 0.1921 & 1.96 \\
3 & 1.0  & 43.37 & 0.9989 & 0.0230 & 3.12 \\
4 & 1.5  & 13.79 & 1.0082 & 0.0737 & 3.16 \\
5 & 2.0  & 21.92 & 1.0118 & 0.0467 & 3.14 \\
\bottomrule
\end{tabular}

\vspace{0.5em}
Comments: Best result at scale 0.75. Poor convergence at higher scales.

\section*{Method 2: DFP}
\textbf{General Behavior:} DFP displayed erratic behavior and was occasionally unstable due to nearly singular updates. Best performance was observed for scale = 1.0, though convergence was still suboptimal.

\begin{tabular}{cccccc}
\toprule
Run & Scale & Distance to $\mathbf{x}^*$ & $\ell_k$ & $q_k$ & Runtime (s) \\
\midrule
1 & 0.5  & 4.37  & 1.0000 & 0.2286 & 2.05 \\
2 & 0.75 & 7.22  & 1.0006 & 0.1387 & 3.13 \\
3 & 1.0  & 4.09  & 0.9961 & 0.2424 & 0.51 \\
4 & 1.5  & 14.92 & 1.0065 & 0.0679 & 3.21 \\
5 & 2.0  & 31.87 & 1.0039 & 0.0316 & 3.14 \\
\bottomrule
\end{tabular}

\vspace{0.5em}
Comments: Best result at scale 1.0. Unstable behavior at large scales.

\section*{Method 3: SR1}
\textbf{General Behavior:} SR1 offered consistent performance at smaller scales and achieved decent proximity to $\mathbf{x}^*$, especially in Run 3. It was, however, slightly less stable at larger initializations.

\begin{tabular}{cccccc}
\toprule
Run & Scale & Distance to $\mathbf{x}^*$ & $\ell_k$ & $q_k$ & Runtime (s) \\
\midrule
1 & 0.5  & 4.09  & 1.0027 & 0.2457 & 1.99 \\
2 & 0.75 & 4.51  & 1.0262 & 0.2332 & 1.99 \\
3 & 1.0  & 4.46  & 1.0000 & 0.2243 & 1.98 \\
4 & 1.5  & 8.94  & 0.9428 & 0.0995 & 2.03 \\
5 & 2.0  & 29.85 & 1.0341 & 0.0358 & 2.01 \\
\bottomrule
\end{tabular}

\vspace{0.5em}
Comments: Best result at scale 1.0. Divergence at large scales.

\section*{Analysis}
\begin{itemize}
  \item The BFGS method with scale = 0.75 yielded the best results overall, achieving the smallest distance to $\mathbf{x}^*$ and demonstrating stable convergence.
  \item SR1 showed consistent but slower convergence, with less divergence compared to DFP.
  \item DFP occasionally skipped updates due to near-zero curvature conditions, making it less reliable.
  \item All methods benefit from careful tuning of the initial guess; larger scales ($\geq 1.5$) generally degraded performance.
\end{itemize}

\end{document}
